When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-02 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
set papaja options

  library(bibtex)       # for referencing, "bibtex" package
  library(here)         # for path independent file referencing, "here" package
  library(papaja)       # APA conform output, "papaja" package
  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
  library(interactions) # for simple slopes plots, "interactions" package
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package

>>>>

  library(bibtex)       # for referencing, "bibtex" package
  library(here)         # for path independent file referencing, "here" package
  library(papaja)       # APA conform output, "papaja" package
  options(papaja.na_string = "")
  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
  library(interactions) # for simple slopes plots, "interactions" package
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package
